Preliminary Thesis Defence

### 2013-11-14 draft.Rnw
added south-africa, r code not running

\mainmatter
\chapter{South Africa}
a la duflo

@@

\section{Modelling probabilistic beliefs for single agents as
distributions, incorporating changes and apparent incommensurability.}

\section{Abstract}

By constructing a distribution of the belief structure of a single
agent, we can mitigate seemingly incommensurable beliefs. This paper
proposes to generalise the concept of a single agents beliefs, from a
point estimate to a distributional approximation. This will allow us to
deal with differing estimates of the probability \emph{p}, as well as
with estimates of \emph{p} and \emph{¬p} violating unitarity, in
meaningful way. Additionally with a distributional approximation, we can
estimate agents' beliefs, using the state which they are in.

@@

\chapter{Police Reform Conkary}
\subfile{conakry.tex}

\chapter{Bitcoin remitances}
\subfile{bitcoin.tex}

\chapter{Rare events}
black swans, dragon king

\begin{refsection}
\subfile{morrisShin.tex}
\parencite{morris1998unique}
\printbibliography
\end{refsection}

>>>>

\mainmatter

\subfile{south-africa.tex}

@@

\section*{Abstract}
By constructing a distribution of the belief structure of a single
agent, we can mitigate seemingly incommensurable beliefs. This paper
proposes to generalise the concept of a single agents beliefs, from a
point estimate to a distributional approximation. This will allow us to
deal with differing estimates of the probability \emph{p}, as well as
with estimates of \emph{p} and \emph{¬p} violating unitarity, in
meaningful way. Additionally with a distributional approximation, we can
estimate agents' beliefs, using the state which they are in.

@@

\begin{refsection}
\chapter{Morris Shin Currency Attacks}
\subfile{morrisShin.tex}
\parencite{morris1998unique}
\printbibliography
\end{refsection}

### 2013-11-14 south-africa.tex
added south-africa, r code not running

Additional South African Evidence on Pensions and Child Growth
==============================================================
Bastiaan Quast
--------------------------------------------------------------

Abstract
--------------------------------------------------------------
In this paper I look at the effect of the gender of pension recipients on the growth of children in the same households.

@@

Introduction
--------------------------------------------------------------
This paper looks at the effect of the gender of pension recipients on the growth of children in their household in South Africa. The approach is very similar to Duflo ([2000][1],[2003][2]). The deviation from international standards [Child Growth Standards][6] for weight-for-height and length-for-age are computed as z-scores. These are then compared for different pension recipient status.

@@

Duflo finds evidence in South Africa's 1993 [Integrated Household Survey][3] that girls' short term nutrition (weight-for-height) was positively influence by living with the maternal grandmother if the grandmother was eligible for a state pension. This is directly after the significant increase in the pension sum for blacks. The pension-eligibility age at this time was 60 for women and 65 for men.

This study deviates from the Duflo study in several ways. In 2008 and 2012 the first and second wave of the [National Income Dynamics Study][4] have gathered similar data. In the period 2008-2010, the government lowered the eligibility age for men from 65 to 60 ([Announcement][5]).

@@

Another deviation is the usage of [Child Growth Standards][6] in stead of CDC's, since these have superseded the CDC charts, however this should not be of any consequence.

The main preliminary result is that the household effect (i.e. having one or more recipients in the household) is very insignificant in the 2008 estimate. But in the 2012 estimate it is very significant.

Data
--------------------------------------------------------------
In this paper I use data from two sources. The first is the South African National Income Dynamics Survey  and the second is the World Health Organization's Child Growth Standards [Child Growth Standards][6].

@@

In 2006 the WHO published its standards for child growth [Child Growth Standards][6]. These standards are based on the scores of children from different ethnic populations in households which observed a healthy lifestyle. The standards provide the means and standards deviations used. These are on a monthly basis for height-for-age, and on a semi-centimeter level for weight-for-height scores.

```{r, include=FALSE}
load("w1w2.RData")
library(sem)
library(ggplot2)
```

```{r}
p1 <- ggplot(subset(w1_child,w1_woman_60 == 1), aes(w1_c_age_m, w1_zhfa, colour=factor(w1_c_woman)))
p1 + stat_smooth(method="loess")# + geom_point()
```

Results
--------------------------------------------------------------
Basic HAZ (2008).
```{r}
summary(w1_haz0)
```

HAZ 2008, with 2012 eligiblity as an IV
```{r}
summary(tsls_w1w2_haz0)
```

HAZ 2008, with 2012 eligiblity as an IV (men over 65 only)
```{r}
summary(tsls_w1w2_haz1)
```

  [1]: http://www.jstor.org/discover/10.2307/117257         "Child Health and Household Resources in South Africa"
  [2]: http://wber.oxfordjournals.org/content/17/1/1        "Grandmothers and Granddaughters"
  [3]: http://microdata.worldbank.org/index.php/catalog/297 "Integrated Household Survey"
  [4]: http://www.nids.uct.ac.za/home/                      "National Income Dynamics Study"
  [5]: http://www.southafrica.info/services/government/pension-160708.htm
  [6]: http://www.who.int/childgrowth/en/                   "Child Growth Standards"
  [7]: http://www.who.int/nutgrowthdb/en/                   "Global Database on Child Growth and Malnutrition"

>>>>

\documentclass[draft.tex]{subfiles}

\begin{document}

\chapter{Additional South African Evidence on Pensions and Child Growth}

\section{Abstract}

In this paper I look at the effect of the gender of pension recipients
on the growth of children in the same households.

@@

\section{Introduction}

This paper looks at the effect of the gender of pension recipients on
the growth of children in their household in South Africa. The approach
is very similar to Duflo
(\href{http://www.jstor.org/discover/10.2307/117257}{2000},\href{http://wber.oxfordjournals.org/content/17/1/1}{2003}).
The deviation from international standards
\href{http://www.who.int/childgrowth/en/}{Child Growth Standards} for
weight-for-height and length-for-age are computed as z-scores. These are
then compared for different pension recipient status.

@@

Duflo finds evidence in South Africa's 1993
\href{http://microdata.worldbank.org/index.php/catalog/297}{Integrated
Household Survey} that girls' short term nutrition (weight-for-height)
was positively influence by living with the maternal grandmother if the
grandmother was eligible for a state pension. This is directly after the
significant increase in the pension sum for blacks. The
pension-eligibility age at this time was 60 for women and 65 for men.

This study deviates from the Duflo study in several ways. In 2008 and
2012 the first and second wave of the
\href{http://www.nids.uct.ac.za/home/}{National Income Dynamics Study}
have gathered similar data. In the period 2008-2010, the government
lowered the eligibility age for men from 65 to 60
(\href{http://www.southafrica.info/services/government/pension-160708.htm}{Announcement}).

@@

Another deviation is the usage of
\href{http://www.who.int/childgrowth/en/}{Child Growth Standards} in
stead of CDC's, since these have superseded the CDC charts, however this
should not be of any consequence.

The main preliminary result is that the household effect (i.e.~having
one or more recipients in the household) is very insignificant in the
2008 estimate. But in the 2012 estimate it is very significant.

\section{Data}

In this paper I use data from two sources. The first is the South
African National Income Dynamics Survey and the second is the World
Health Organization's Child Growth Standards
\href{http://www.who.int/childgrowth/en/}{Child Growth Standards}.

@@

In 2006 the WHO published its standards for child growth
\href{http://www.who.int/childgrowth/en/}{Child Growth Standards}. These
standards are based on the scores of children from different ethnic
populations in households which observed a healthy lifestyle. The
standards provide the means and standards deviations used. These are on
a monthly basis for height-for-age, and on a semi-centimeter level for
weight-for-height scores.

\texttt{\{r, include=FALSE\} load("w1w2.RData") library(sem) library(ggplot2)}

\texttt{\{r\} p1 \textless{}- ggplot(subset(w1\_child,w1\_woman\_60 == 1), aes(w1\_c\_age\_m, w1\_zhfa, colour=factor(w1\_c\_woman))) p1 + stat\_smooth(method="loess")\# + geom\_point()}

\section{Results}

Basic HAZ (2008). \texttt{\{r\} summary(w1\_haz0)}

HAZ 2008, with 2012 eligiblity as an IV
\texttt{\{r\} summary(tsls\_w1w2\_haz0)}

HAZ 2008, with 2012 eligiblity as an IV (men over 65 only)
\texttt{\{r\} summary(tsls\_w1w2\_haz1)}

\end{document}
